### 2021-10-28 README.Rmd
update readme with publication

[![Run Tests](https://github.com/BrunaLab/HeliconiaDemography/actions/workflows/run-testthat.yaml/badge.svg)](https://github.com/BrunaLab/HeliconiaDemography/actions/workflows/run-testthat.yaml)

@@

This repository contains the data and code for a manuscript written for submission to Global Change Biology tentatively titled: "Delayed effects of climate on vital rates leads to demographic divergence in Amazonian forest fragments"

@@

**Using HPC**:
You may need to install packages on the remote HPC if using `tar_make_clustermq()` with the SSH option.  Unfortunately, I'm not sure if there is an easy way to do this using `renv`. You should, however, make sure the same versions of the packages are installed locally and on the HPC, especially `gratia` which I'm using a development version of that has important bugs fixed, but not new bugs introduced.

@@

<!--
### Licenses
-->
<!-- **Text and figures :** [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/) -->

<!-- <!-- **Code :** See the [DESCRIPTION](DESCRIPTION) file -->

<!-- **Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse -->

>>>>

[![Run Tests](https://github.com/BrunaLab/HeliconiaDemography/actions/workflows/run-testthat.yaml/badge.svg)](https://github.com/BrunaLab/HeliconiaDemography/actions/workflows/run-testthat.yaml) [![Zenodo DOI](https://zenodo.org/badge/289078614.svg)](https://zenodo.org/badge/latestdoi/289078614) [![Paper DOI](https://img.shields.io/badge/DOI-10.1111%2Fgcb.15900-blue)](https://doi.org/10.1111/gcb.15900)

@@

This repository contains the data and code for:

Scott ER, Uriarte M, Bruna EM (2021) Delayed effects of climate on vital rates lead to demographic divergence in Amazonian forest fragments. Global Change Biology. https://doi.org/10.1111/gcb.15900

## How to cite

If you use the data or code in this repository, please cite the [Zenodo archive](https://zenodo.org/badge/latestdoi/289078614) as well as the Global Change Biology [paper](https://doi.org/10.1111/gcb.15900).

@@

@@
